Manuscript draft

### 2019-08-26 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

>>>>

Limitations: 
- We have only considered mature forests; there is a lot more work to go towards understanding the effect of stand age on productivity. In part, understanding these patterns will be reliant on acquiring more data at all stand ages.
- We have standardised data as far as possible; however there are still challenges with ensuring data quality is as high as possible. For example, there are inherent challenges with measuring stand-level productivity, particularly for certain components. Standardising BNPP in particular is challenging, as it is often sampled to insufficient depth/extrapolated from measures of ANPP. This means that, although we have been careful to control data selection within the database, we cannot entirely control the quality of data going into the database. As a result, our results are likely to be affected by this.
- As above, we are looking at climate data at a coarse scale; these are generalisations about large-scale patterns. Stand-level studies will help to improve our understanding of the effect of climate on productivity on smaller spatial and temporal scales.

Our findings support a lot of previous work that has been done, but we are doing this with a much larger and more comprehensive dataset, with better standardisation of available data.
